Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-30 main.tex
Added tikz picture for the whole algorithms steps as requested - basically a summary of the three algorithms given in the same section - still need to write the text for the algorithm section, and specify the assumptions/shorthand notation in the algorithms and picture Added synctex file to gitignore

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
%\usepackage{microtype}

% User local packages
\usepackage{ISASmacros/isasmathmacros}

@@

@@

    % Gray range circles
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \draw[gray!50] (s1) circle (\srange);
        \draw[gray!50] (s2) circle (\srange);
        \draw[gray!50] (s3) circle (\srange);
        \draw[gray!50] (s4) circle (\srange);
        \draw[gray!50] (s5) circle (\srange);
    \end{scope}
    % Red subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[red!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Blue subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \fill[blue!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Magenta double overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[magenta!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Sensors
    \fill[black] (s1) circle (\sradius);
    \fill[black] (s2) circle (\sradius);
    \fill[black] (s3) circle (\sradius);
    \fill[black] (s4) circle (\sradius);
    \fill[black] (s5) circle (\sradius);
    % Bounding box
    \draw[gray] (brect_start) rectangle (brect_end);
    % Navigator
    \clip (brect_start) rectangle (brect_end);
    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
        % Plane
        \draw[fill]  plot[smooth, tension=.6] coordinates {
        (-0.65,-0.9) 
        (-0.6,-0.85) 
        (-0.4,-0.75) 
        (-0.25,-0.65) 
        (-0.15,-0.5) 
        (-0.12,-0.3) 
        (-0.10,-0.1) 
        (0.0,0.0) 
        (0.10,-0.1) 
        (0.12,-0.3) 
        (0.15,-0.5) 
        (0.25,-0.65) 
        (0.4,-0.75) 
        (0.6,-0.85) 
        (0.65,-0.9)
        } -- plot[smooth, tension=.6] coordinates {
        (0.65,-0.9) 
        (0.15,-0.91)
        (0.35,-1.1) 
        (0.37,-1.15)
        } -- plot[smooth, tension=.6] coordinates {
        (0.37,-1.15)
        (0.0,-1.12) 
        (-0.37,-1.15) 
        } -- plot[smooth, tension=.6] coordinates {
        (-0.37,-1.15)
        (-0.35,-1.1) 
        (-0.15,-0.91) 
        (-0.65,-0.9) 
        } -- cycle;
        % Trail
        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
    \end{scope}
    % Sensor labels
    \node[label=1] at (s1) {};
    \node[label=2] at (s2) {};
    \node[label=3] at (s3) {};
    \node[label=4] at (s4) {};
    \node[label=5] at (s5) {};
\end{tikzpicture}
\caption{An example of sensor subsets; $\{1,2,3\}$ and $\{3,4,5\}$, and the areas where the navigator is in range of all sensors within a subset.}
\label{fig:sensor_subsets}
\end{figure}

@@

>>>>

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}

% Local packages
\usepackage{ISASmacros/isasmathmacros}

@@

% Tikz reused pics
\tikzset{
   plane/.pic = {
    \draw[fill]  plot[smooth, tension=0.6] coordinates {
        (-0.65,-0.9) 
        (-0.6,-0.85) 
        (-0.4,-0.75) 
        (-0.25,-0.65) 
        (-0.15,-0.5) 
        (-0.12,-0.3) 
        (-0.1,-0.1) 
        (0,0) 
        (0.1,-0.1) 
        (0.12,-0.3) 
        (0.15,-0.5) 
        (0.25,-0.65) 
        (0.4,-0.75) 
        (0.6,-0.85) 
        (0.65,-0.9)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.65,-0.9) 
        (0.15,-0.91)
        (0.35,-1.1) 
        (0.37,-1.15)
        } -- plot[smooth, tension=0.6] coordinates {
        (0.37,-1.15)
        (0,-1.12) 
        (-0.37,-1.15) 
        } -- plot[smooth, tension=0.6] coordinates {
        (-0.37,-1.15)
        (-0.35,-1.1) 
        (-0.15,-0.91) 
        (-0.65,-0.9) 
        } -- cycle;
   }
}

@@

    % Gray range circles
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \draw[gray!50] (s1) circle (\srange);
        \draw[gray!50] (s2) circle (\srange);
        \draw[gray!50] (s3) circle (\srange);
        \draw[gray!50] (s4) circle (\srange);
        \draw[gray!50] (s5) circle (\srange);
    \end{scope}
    % Red subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[red!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Blue subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \fill[blue!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Magenta double overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[magenta!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Sensors
    \fill[black] (s1) circle (\sradius);
    \fill[black] (s2) circle (\sradius);
    \fill[black] (s3) circle (\sradius);
    \fill[black] (s4) circle (\sradius);
    \fill[black] (s5) circle (\sradius);
    % Bounding box
    \draw[gray] (brect_start) rectangle (brect_end);
    % Navigator
    \clip (brect_start) rectangle (brect_end);
    \pic[rotate=-40,xscale=0.22,yscale=0.3] at (nav_loc) {plane};
    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
        % Trail
        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
    \end{scope}
    % Sensor labels
    \node[label=1] at (s1) {};
    \node[label=2] at (s2) {};
    \node[label=3] at (s3) {};
    \node[label=4] at (s4) {};
    \node[label=5] at (s5) {};
\end{tikzpicture}
\caption{An example of sensor subsets; $\{1,2,3\}$ and $\{3,4,5\}$, and the areas where the navigator is in range of all sensors within a subset.}
\label{fig:sensor_subsets}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Prediction
    \draw  (0,1.75) rectangle (8,8);
    \node at (4,7.5) {\small 1. Prediction};

    % Navigator
    \fill  [blue!40] (3.25,7) rectangle (4.75,5.5);
    \pic[xscale=0.22,yscale=0.3] at (4,6.6725) {plane};
    \node at (4,5.875) {$\rvec{x}_k$, $\mat{P}_k$};

    % Sensors
    \fill  (1.5,3) [red!40] ellipse (0.5 and 0.5);
    \node at (1.5,2.25) {Sensor $1$};
    \fill  (6.5,3) [red!40] ellipse (0.5 and 0.5);
    \node at (6.5,2.25) {Sensor $n$};

    \fill [black] (3.5,3) circle (0.05);
    \fill [black] (4,3) circle (0.05);
    \fill [black] (4.5,3) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.75,5.25) (1.75,3.5)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(4.25,5.25) (6.25,3.5)};

    \fill [lightgray]  (0.25,4.75) rectangle (7.75,3.75);
    \node at (4,4.25) {$\langle\mathcal{E}_{pk_0}(\rv{\omega}): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k\rv{y}_k, \rv{x}_k, \rv{y}_k\}\rangle$};

    % Measurement
    \draw  (0,-4.75) rectangle (8,1.5);
    \node at (4,1) {\small 2. Measurement};

    % Navigator
    \fill  (4,0) [blue!40] ellipse (0.5 and 0.5);
    \pic[xscale=0.22,yscale=0.3] at (4,0.1725) {plane};

    % Sensors
    \fill  [red!40] (7.5,-3.75)  rectangle (5.5,-2.75);
    \node at (1.5,-4.25) {Sensor $1$};
    \fill  [red!40] (2.5,-3.75)  rectangle (0.5,-2.75);
    \node at (6.5,-4.25) {Sensor $n$};

    \node at (1.5,-3.25) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
    \node at (6.5,-3.25) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};

    \fill [black] (3.5,-3.25) circle (0.05);
    \fill [black] (4,-3.25) circle (0.05);
    \fill [black] (4.5,-3.25) circle (0.05);

    % Arrows
    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,-2.5) (3.75,-0.75)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(6.25,-2.5) (4.25,-0.75)};

    \fill [lightgray]  (0.25,-1.25) rectangle (3.75,-2.25);
    \node at (2,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,1})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,1})$};
    \fill [lightgray]  (4.25,-1.25) rectangle (7.75,-2.25);
    \node at (6,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,n})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,n})$};

    % Update
    \draw  (0,-10.25) rectangle (8,-5);
    \node at (4,-5.5) {\small 3. Update};

    % Navigator
    \fill  [blue!40] (2.25,-6) rectangle (5.75,-8);
    \pic[xscale=0.22,yscale=0.3] at (4,-6.3275) {plane};
    \node at (4,-7.125) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
    \node at (4,-7.625) {$\rvec{x}_k$, $\mat{P}_k$};

    % Sensors
    \fill  (6.5,-9) [red!40] ellipse (0.5 and 0.5);
    \node at (1.5,-9.75) {Sensor $1$};
    \fill  (1.5,-9) [red!40] ellipse (0.5 and 0.5);
    \node at (6.5,-9.75) {Sensor $n$};

    \fill [black] (3.5,-9) circle (0.05);
    \fill [black] (4,-9) circle (0.05);
    \fill [black] (4.5,-9) circle (0.05);

\end{tikzpicture}
\vspace{\baselineskip}
\caption{Alg summary}
\label{fig:agg_steps}
\end{figure}
